method

### 2022-02-09 06_Paper/ER-ED/method.Rmd
fixed columns

SubjArousalView_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
                                                          df_error = SubjArousalView_con$df,
                                                          ci = 0.95,
                                                          digits = 2))

@@

SubjArousalReg_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
                                                         df_error = SubjArousalReg_con$df,
                                                         ci = 0.95),
                                   digits = 2)

@@

SubjEffort_con$etasq <- format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                         df_error = SubjEffort_con$df,
                                                         ci = 0.95),
                                   digits = 2)

>>>>

SubjArousalView_con <- cbind(SubjArousalView_con,
                             format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
                                                          df_error = SubjArousalView_con$df,
                                                          ci = 0.95),
                                                          digits = 2))

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

@@

SubjArousalReg_con <- cbind(SubjArousalReg_con,
                            format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
                                                         df_error = SubjArousalReg_con$df,
                                                         ci = 0.95),
                                   digits = 2))

colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

@@

SubjEffort_con <- cbind(SubjEffort_con,
                        format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                         df_error = SubjEffort_con$df,
                                                         ci = 0.95),
                                   digits = 2))

colnames(SubjEffort_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
